Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-01-16 paper/sheaf_lics.tex
add some theorems about modalities

@@

% We use the following definition of truncated left exact modalities:
\begin{defi}
  \label{sec:defin-basic-prop-1}
  Let $n\geq -1$ be a truncation index. A left exact modality at level
  $n$ is the data of
  \begin{enumerate}[(i)]
  \item A predicate $P:\Type_p \to \HProp$
  \item For every $n$-truncated type $A$, a $n$-truncated type
    $\modal A$ such that $P(\modal A)$
  \item For every $n$-truncated type $A$, a map $\eta_A:A \to
    \modal A$
  \end{enumerate}
  such that
  \begin{enumerate}[(i)]
    \setcounter{enumi}{3}
  \item For every $n$-truncated types $A$ and $B$, if $P(B)$ then
    $$\left\{
      \begin{array}{rcl}
        (\modal A \to B) & \to & (A \to B) \\
        f & \mapsto & f \circ \eta_A
      \end{array} \right.$$
    is an equivalence.
  \item for any $A:\Type_p$ and $B:A \to \Type_p$ such that $P(A)$
    and $\prod_{x:A} P(B x)$, then $P\left( \sum_{x:A} B(x)\right)$
  \item for any $A:\Type_p$ and $x,y:A$, if $\modal A$ is
    contractible, then $\modal (x=y)$ is contractible.
  \end{enumerate}
  Conditions (i) to (iv) define a {\em reflective subuniverse}, (i) to
  (v) a {\em modality}.
\end{defi}

@@

\begin{prop}

stability properties
\vspace{1em}

@@

\item
$\modal \one =\one $
\item
Stability under product and dependent product (7.7.2 of \cite{hottbook})
\item
 In particular, if $X:\Type_p$ verifies
$P(X)$, then for any $x,y:X$, $P(x=y)$.
\item
Another useful property is that we can extend property {\it (iii)} to
dependent product.
\end{itemize}
\end{prop}

@@

Moreover the following diagram commute
$$\xymatrix{
  \sum_{x:X} (f x = y) \ar[r]^\eta \ar[d]_\gamma & \modal \left(\sum_{x:X}  (f x = y)\right) \ar@{=}[dl]\\
  \sum_{x:\modal X} (\modal f x = \eta_Y y) &
}$$
where $\pi_1 \circ \gamma = \eta_X \circ \pi_1$, and $\pi_2 \circ
\gamma$ is given by the modalisation of paths.
\end{prop}
\begin{proof}
\nt{ça a du sens de mettre une preuve, non ? c'est non trivial et
  nouveau par rapport aux travaux sur les modalités. Ou alors c'est
  la preuve de Shulman qui tu n'as pas faite. En tout cas, il faut clarifier.}
\end{proof}

>>>>

Now, let a map $f:A\to B$ be called {\em (-1)-truncated} if
every fibers of $f$ is an $\HProp$, and {\em
  (-1)-connected} if every fibers $f$ is merely
inhabited, \ie such that $\|\fib f y\|$ for all $y$.

\begin{defi}
  Let $f:A\to B$ be a function. The {\em image} of $f$ is
  $$\im(f) = \sum_{y:B} \|\fib f y\|.$$
\end{defi}

It is then fairly obvious that the canonical function $\hat f : A \to
\im(f)$ is (-1)-connected, thus the following proposition arise
(\cite{hottbook}, Lemma 7.6.4)~:
\begin{prop}
  An map $f:A\to B$ factors as a (-1)-connected function followed by a
  (-1)-truncated function.
\end{prop}

@@

% We use the following definition of truncated left exact modalities:
\begin{defi}
  \label{sec:defin-basic-prop-1}
  Let $n\geq -1$ be a truncation index. A left exact modality at level
  $n$ is the data of
  \kq{Do you prefer $n$ over $p$ ?}
  \begin{enumerate}[(i)]
  \item A predicate $P:\Type_p \to \HProp$
  \item For every $n$-truncated type $A$, a $n$-truncated type
    $\modal A$ such that $P(\modal A)$
  \item For every $n$-truncated type $A$, a map $\eta_A:A \to
    \modal A$
  \end{enumerate}
  such that
  \begin{enumerate}[(i)]
    \setcounter{enumi}{3}
  \item For every $n$-truncated types $A$ and $B$, if $P(B)$ then
    $$\left\{
      \begin{array}{rcl}
        (\modal A \to B) & \to & (A \to B) \\
        f & \mapsto & f \circ \eta_A
      \end{array} \right.$$
    is an equivalence.
  \item for any $A:\Type_p$ and $B:A \to \Type_p$ such that $P(A)$
    and $\prod_{x:A} P(B x)$, then $P\left( \sum_{x:A} B(x)\right)$
  \item for any $A:\Type_p$ and $x,y:A$, if $\modal A$ is
    contractible, then $\modal (x=y)$ is contractible.
  \end{enumerate}
  Conditions (i) to (iv) define a {\em reflective subuniverse}, (i) to
  (v) a {\em modality}.
\end{defi}

@@

\begin{prop}
\vspace{1em}

@@

\item $\one$ seen as a $\Type_p$ is modal, ie $\modal \one =\one$.
\item (\cite{hottbook}, Lemma 7.7.2)
  Let $A:\Type$ and $B:A \to \Type_p^\modal$. Then $P\left(\prod_{a:A} (B\,
  a)\right)$. 
\item (\cite{hottbook}, Corollary 7.7.2) For any $A,B:\Type_p$,
  $\modal (A\times B) = (\modal A) \times (\modal B)$.
\item Let $A:\Type_p\modal$. Then for any $x,y:X$, $P(x=y)$.
\item (\cite{hottbook}, Theorem 7.7.4) 
  {\it (iv} can be extended to dependent product. Precisely~:

  Let $A:\Type_p$ and $B:\modal A \to \Type_p^\modal$. For any map
  $g:\prod_{a:A} B(\eta_A(a))$ there exists a map $f:\prod_{z:\modal
    A} (B\, z)$ such that for all $a:A$, $f(\eta_A(a)) = g(a)$.
\end{itemize}
\end{prop}

@@

Moreover the following diagram commute
$$\xymatrix{
  \sum_{x:X} (f x = y) \ar[r]^\eta \ar[d]_\gamma & \modal \left(\sum_{x:X}  (f x = y)\right) \ar@{=}[dl]\\
  \sum_{x:\modal X} (\modal f x = \eta_Y y) &
}$$
where $\pi_1 \circ \gamma = \eta_X \circ \pi_1$, and $\pi_2 \circ
\gamma$ is given by the modalisation of paths.
\end{prop}
\begin{proof}
\nt{ça a du sens de mettre une preuve, non ? c'est non trivial et
  nouveau par rapport aux travaux sur les modalités. Ou alors c'est
  la preuve de Shulman qui tu n'as pas faite. En tout cas, il faut
  clarifier.}

The central result used here is the following
\begin{lem}
  Let $X:\Type_p$, $Y:\Type_p\modal$ and $f:X\to Y$. If for all $y:Y$,
  $\modal (\fib f y)$ is contractible, then $\modal X = Y$.
\end{lem}

Here, $\sum_{x:\modal X} (\modal f x = \eta_Y y)$ is modal, thus we
can define $$f:\modal \left(\sum_{x:X}  (f x = y)\right) \to
\sum_{x:\modal X} (\modal f x = \eta_Y y).$$
We need to check that the image of its fibers by $\modal$ are
contractible.
\kq{Finish that}
\end{proof}
